The Hot Hand Fallacy in Call of Duty Search and Destroy

### 2022-08-30 paper/paper.Rmd
discussion

Perhaps it is not surprising that we did not find evidence in favor of the hot hand effect given the small "skill gap" in CoD relative to other esports that most CoD players themselves would describe, despite such a confession being potentially humiliating [@tacticalrab2022]. A small skill gap fosters randomness in outcomes, implying that a given team is less likely to go on streaks of consecutive round wins in SnD, compared to the counterfactual setting where the skill gap is "large" and better teams consistently defeat worse teams.

For the sake of brevity, we did not account for offensive or defensive role when considering win proportions in the rounds immediately following streaks. It would be interesting to look at whether the round win percentage is higher after streaks of round wins when the team starts the streak as the offensive team. Considering streaks of three, this would mean that the streaking team would be playing defense in the round immediately following the last streak win. Knowing that teams are more likely to win on defense---note that $1 - \bar{\tau} = 52.2%$---we should expect that teams on such streaks are more likely to win the round than teams that go on streaks of three starting with a defensive round win. On the other hand, streaks of three starting with an offensive round win are less likely to occur than such streaks starting with a defensive win---$\bar{\tau}^2 (1 - \bar{\tau}) \approx$ 11.9% in the former case and $\bar{\tau} (1 - \bar{\tau})^2 \approx$ 13.0% in the latter case---so we would need to properly account for sample size differences.

Another idea would be to account for the quality of the teams. Even if we still cannot prove that the hot hand effect exists when doing so, a null finding would be insightful in and of itself.

>>>>

Perhaps it is not surprising that we did not find evidence in favor of the hot hand effect given the small "skill gap" in CoD relative to other esports, fostering more randomness in outcomes [@tacticalrab2022]. More parity suggests that a given team is less likely to go on streaks of consecutive round wins in SnD compared to the counterfactual setting with a larger skill gap, where better teams more consistently defeat worse teams. On the other hand, one can argue that more parity does not necessarily imply that streaks of wins are more unlikely to occur, particularly when controlling for team ability.[^26]

[^26]: Lopez et al. [-@lopez2018] found that, when accounting for team strength and temporal factors, game outcomes in the NHL and the MLB are more random than those in the NFL and the NBA, implying that the NHL and MLB are more competitive; and Chance found that no choice of a constant game probability could properly explain the distribution of games played in championships series for the NHL and the MLB. Together, their conclusions suggest that more parity does not necessarily preclude streaky outcomes.

For the sake of brevity, we did not account for offensive or defensive role when considering win proportions in the rounds immediately following streaks. It would be interesting to look at whether the round win percentage is higher after streaks of round wins when the team starts the streak as the offensive team. Considering streaks of three, this would mean that the streaking team would be playing defense in the round immediately following the last streak win. Knowing that teams are more likely to win on defense---note that $1 - \bar{\tau}$ = 52.2%---we should expect that teams on such streaks are more likely to win the round than teams that go on streaks of three starting with a defensive round win. On the other hand, streaks of three starting with an offensive round win are less likely to occur than such streaks starting with a defensive win---$\bar{\tau}^2 (1 - \bar{\tau}) \approx$ 11.9% in the former case and $\bar{\tau} (1 - \bar{\tau})^2 \approx$ 13.0% in the latter case---so we would need to properly account for sample size differences.

### 2022-08-30 paper/paper.tex
discussion

\usepackage{amsmath}
\begin{document}
\maketitle

@@

Perhaps it is not surprising that we did not find evidence in favor of
the hot hand effect given the small ``skill gap'' in CoD relative to
other esports that most CoD players themselves would describe, despite
such a confession being potentially humiliating
(\protect\hyperlink{ref-tacticalrab2022}{TacticalRab 2022}). A small
skill gap fosters randomness in outcomes, implying that a given team is
less likely to go on streaks of consecutive round wins in SnD, compared
to the counterfactual setting where the skill gap is ``large'' and
better teams consistently defeat worse teams.

For the sake of brevity, we did not account for offensive or defensive
role when considering win proportions in the rounds immediately
following streaks. It would be interesting to look at whether the round
win percentage is higher after streaks of round wins when the team
starts the streak as the offensive team. Considering streaks of three,
this would mean that the streaking team would be playing defense in the
round immediately following the last streak win. Knowing that teams are
more likely to win on defense---note that \(1 - \bar{\tau} = 52.2%
\)---we should expect that teams on such streaks are more likely to win
the round than teams that go on streaks of three starting with a
defensive round win. On the other hand, streaks of three starting with
an offensive round win are less likely to occur than such streaks
starting with a defensive
win---\(\bar{\tau}^2 (1 - \bar{\tau}) \approx\) 11.9\% in the former
case and \(\bar{\tau} (1 - \bar{\tau})^2 \approx\) 13.0\% in the latter
case---so we would need to properly account for sample size differences.

Another idea would be to account for the quality of the teams. Even if
we still cannot prove that the hot hand effect exists when doing so, a
null finding would be insightful in and of itself.

@@

>>>>

\usepackage{amsmath}
\usepackage[bottom]{footmisc}
\begin{document}
\maketitle

@@

Perhaps it is not surprising that we did not find evidence in favor of
the hot hand effect given the small ``skill gap'' in CoD relative to
other esports, fostering more randomness in outcomes
(\protect\hyperlink{ref-tacticalrab2022}{TacticalRab 2022}). More parity
suggests that a given team is less likely to go on streaks of
consecutive round wins in SnD compared to the counterfactual setting
with a larger skill gap, where better teams more consistently defeat
worse teams. On the other hand, one can argue that more parity does not
necessarily imply that streaks of wins are more unlikely to occur,
particularly when controlling for team ability.\footnote{Lopez et al.
  (\protect\hyperlink{ref-lopez2018}{2018}) found that, when accounting
  for team strength and temporal factors, game outcomes in the NHL and
  the MLB are more random than those in the NFL and the NBA, implying
  that the NHL and MLB are more competitive; and Chance found that no
  choice of a constant game probability could properly explain the
  distribution of games played in championships series for the NHL and
  the MLB. Together, their conclusions suggest that more parity does not
  necessarily preclude streaky outcomes.}

For the sake of brevity, we did not account for offensive or defensive
role when considering win proportions in the rounds immediately
following streaks. It would be interesting to look at whether the round
win percentage is higher after streaks of round wins when the team
starts the streak as the offensive team. Considering streaks of three,
this would mean that the streaking team would be playing defense in the
round immediately following the last streak win. Knowing that teams are
more likely to win on defense---note that \(1 - \bar{\tau}\) =
52.2\%---we should expect that teams on such streaks are more likely to
win the round than teams that go on streaks of three starting with a
defensive round win. On the other hand, streaks of three starting with
an offensive round win are less likely to occur than such streaks
starting with a defensive
win---\(\bar{\tau}^2 (1 - \bar{\tau}) \approx\) 11.9\% in the former
case and \(\bar{\tau} (1 - \bar{\tau})^2 \approx\) 13.0\% in the latter
case---so we would need to properly account for sample size differences.

@@

\leavevmode\vadjust pre{\hypertarget{ref-lopez2018}{}}%
Lopez, Michael J., Gregory J. Matthews, and Benjamin S. Baumer. 2018.
{``How Often Does the Best Team Win? A Unified Approach to Understanding
Randomness in North American Sport.''} \emph{The Annals of Applied
Statistics} 12 (4): 24832516.
